\selectlanguage{english}
\begin{abstract}
\label{sec:abstract}
\setcounter{page}{1}
Unified Communications solutions bring together several communication modes, technologies, and applications in order to answer businesses' and individuals' growing need for simpler, faster, and more effective communications means.
Although many hardware-based products allow the integration of telephony within a computer network environment, telephony features of software-based unified communications solutions are seldom used, which limits their effectiveness or requires another solution to be used jointly.

This master's thesis project aims to demonstrate that unified communications solutions based on Microsoft Lync Server 2013 can effectively address a wide variety of business scenarios, including a traditional telephony system replacement.

The first part of this master's thesis introduces background knowledge about unified communications and associated technologies, as well as the different components of the selected unified communication solution.

The case study presented in this thesis is the first large-scale Lync 2013 deployment with a complete telephony offering in France. The presentation follows the complete deployment process, starting from the analysis of the client's needs to the solution design, construction, and validation.

This project demonstrated the suitability of Lync 2013 as a telephony system replacement. However, the transition from a classic telephony solution to a unified communications solution can be a technical challenge. An essential step in making this transition successful was to take the users' needs into account. It was also essential to accompany these users throughout the transition.

\end{abstract}
%%\clearpage
\selectlanguage{swedish}
%%\chapter*{Sammanfattning}
\begin{abstract}
\label{sec:swedish_abstract}

Samordnad kommunikation (engelska: unified communications) lösningar \linebreak[4]sammanföra flera kommunikationssätt,
teknik och tillämpningar för att besvara företags och individers
växande behovet av enklare, snabbare och mer effektivt kommunikationsmedel.
Även många hårdvara-baserade produkter tillåter \linebreak[4]integration av telefoni
inom ett datornätverk miljö, telefoni funktioner \linebreak[4]mjukvarubaserad
Samordnad kommunikation-lösningar används sällan, vilket begränsar deras effektivitet
eller kräver en annan lösning för att användas gemensamt.
Detta examensarbete syftar till att visa att samordnad kommunikation
lösningar baserade på Microsoft Lync Server 2013 kan effektivt ta itu med en
mängd olika scenarier. Den första delen av detta examensarbete introducerar
bakgrundskunskap om samordnad kommunikation och tillhörande teknologier
liksom de olika komponenterna i den valda samordnad kommunikation
lösning.

Fallstudien som presenteras i denna avhandling är den första storskaliga Lync 2013
utplacering med en komplett telefoni erbjuder i Frankrike. Den presentationen
följer hela implementeringsprocessen, från analys av kundens
kraven till utformning, konstruktion, och validering.
Detta projekt visade \linebreak[4]tillförlitligheten i Lync 2013 som telefoni ersättning
men intyga att även övergången från en klassisk telefoni lösning på ett
samordnad kommunikation-lösning kan vara en teknisk utmaning, ta användarnas
behov i beaktande och medföljande användare genom övergången är kritisk.
\end{abstract}

\selectlanguage{french}
%%\chapter*{Sammanfattning}
\begin{abstract}
\label{sec:french_abstract}

Les solutions de communications unifiées rassemblent différents modes de \linebreak[4] communications, technologies, et applications pour répondre aux besoin croissant des entreprises et individus de méthodes de communications plus simples, rapides et efficaces. Bien que de nombreuses solutions matérielles permettent l'intégration de la téléphonie à un réseau informatique, les fonctions de téléphonie des solutions logicielles sont rarement utilisées, ce qui limite leur efficacité ou nécessite l'utilisation conjointe d'autres solutions.

Ce projet a pour but de démontrer l'efficacité des solutions de communications unifiées basées sur Microsoft Lync 2013 à répondre à une grande variété de besoins professionels, dont le remplacement d'un système de téléphonie traditionnel.

La première partie de ce mémoire introduit les notions nécessaires sur les communications unifiées et les technologies associées, ainsi que les différents composants de la solution de communications unifiées choisie.

L'étude de cas présentée décrit le premier déploiement majeur de Lync Server 2013 comportant une offre de téléphonie complète en France, et suit le processus de déploiement complet, de l'analyse des besoins client à la validation du projet, en passant par la conception, la construction et le test.

Ce projet démontre l'aptitude de Lync en temps que système de téléphonie complet. Cependant la transition d'un système traditionnel à une solution de communications unifiées peut présenter des défis techniques, et il est essentiel de prendre en compte les besoins utilisateurs ainsi que de les accompagner durant la transition.

\end{abstract}

\selectlanguage{english}
\begin{acknowledgements}
ACK
\end{acknowledgements}

\selectlanguage{english}
\tableofcontents

\listoffigures

\listoftables


% \begin{notations}
% \end{notations}

\renewcommand\abbreviationsname{List of Acronyms and Abbreviations}
\begin{abbreviations}
\label{list-of-acronyms-and-abbreviations}


\begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{10em}}

\item[AD] Active Directory
\item[CA] certification authorities

\item[OS] operating system

\item[PBX] private branch exchange
\item[PSTN] public switched telephone network
\item[QoS] Quality of Service
\item[RBAC] role-based access control
\item[SPIT] Spam over Internet Telephony
\item[SSL] Secure Sockets Layer
\item[TLS]  Transport Layer Security

\item[UM] unified messaging

\item[VoIP] voice over IP
\item[WAN]  wide area network
\item[WLAN] wireless local area network
\end{basedescript}
\end{abbreviations}